Self-test prime dimensional EPR pairs with constant alphabet

### 2019-02-07 Draft/draft.tex
Honghao: modified the proofs of Prop.11 and Prop.13

@@

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{EPR^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\G}{G}
\newcommand{\LS}{LS}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}
\newcommand{\dr}[1]{d^{(#1)}}

@@

We use some basic number theory in our work. A primitive root of a prime number
$d$ is an integer $r$ such that $r \pmod{d}$ has multiplicative order $d-1$. Equivalently,
$r$ is the generator of the multiplicative group of integers modulo $d$, $\Z_d^\times$ where
$\Z_d^\times = \{1,2\dots d-1\}$. \textcolor{red}{When the prime number $d$ has multiple primitive roots,
we always work with the smallest one.}
\carl{I'm not clear on what that last sentence means.  You just defined what a primitive root
is --- are you changing the definition now?}

@@

%======================================
\section{The extended weighted CHSH test}
\label{sec:chsh}
%======================================
Before introducing the extended weighted CHSH test, we fill in some background about the weighted CHSH inequality,
namely, that its maximal violation can self-test $2$-dimensional EPR pair and rotated Pauli operators.
The robust self-testing result is summarized in the following theorem.
\begin{theorem}
\label{thm:selftest}
	Suppose the quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]+1}, \{\tilde{B}_y\}_{y \in [2]+1})$ achieves the violation
	at least $2\sqrt{1+\alpha^2} - \epsilon$
	for some $\epsilon$, then
	there exists a local isometry $\Phi = \Phi_A \x \Phi_B$ and an auxiliary state $\ket{aux}$  such that
	\begin{align}
		\| \Phi( \tilde{A}_x \x \tilde{B}_y \ket{\psi}) -\ket{junk} \x (A_x \x B_y) \ket{\EPR{2}}  \| = O((\alpha+\frac{1}{\alpha}) \sqrt{\epsilon})
	\end{align}
	for $x,y \in \{0, 1, 2\}$ where the subscript $0$ refers to the identity operator and $A_x, B_y$ are 
	defined in \cref{def:ideal}.  \carl{You're using both ``aux'' and ``junk'' for the auxilliary state.  Also you need
	to be clearer about what label you are using for Alice's and Bob's systems (see my previous comment on this).}
\end{theorem}
Our approach is very similar to the one used in Ref.~\cite{bamps2015} so we 
defer the proof of \cref{thm:selftest} till \cref{sec:selftest}.
After proving the robust self-testing result, we take one step further and observe an interesting property of the 
product of Bob's observables.
\begin{proposition}
\label{prop:2d-subspace}
	Let $\mu = \arctan(1/\alpha)$ for some $\alpha$.
	Suppose a quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]+1}, \{\tilde{B}_y\}_{y \in [2]+1})$ achieves the maximal 
	violation of  $\I_{\alpha}$, then $\tilde{B}_0\tilde{B}_1$ has eigenvalues $e^{i2\mu}$ and $e^{-i2\mu}$.  \carl{Make clear
	that we mean that these are the only eigenvalues.}
\end{proposition}
\begin{proof}[Proof of \cref{prop:2d-subspace}]
	Following the argument in the proof of \cref{thm:selftest} in \cref{sec:selftest}, we know
	$\tilde{Z}_B = (\tB_1+\tB_2)/2\cos(\mu)$ is a binary observable. \textcolor{red}{HF: Do we need to justify it?}  \carl{Yes,
	you should say more specifically where that is proved.}
	Expanding $\tilde{Z}_B^2$ we get
	\begin{align*}
		\1 = \tilde{Z}_B^2 = \frac{\tB_1^2 + \tB_1\tB_2 + \tB_2\tB_1 + \tB_2^2}{4\cos(\mu)^2}
		=\frac{2\1 + \tB_1\tB_2 + \tB_2\tB_1}{4\cos^2(\mu)},
	\end{align*}
	so we can derive that 
	\begin{align}
	\label{eq:eig_v}
		\tB_1\tB_2 + \tB_2\tB_1 = 2(2\cos^2(\mu)-1)\1 = 2 \cos(2\mu) \1.
	\end{align}
	Observe that $(\tB_1\tB_2)^\dagger = \tB_2\tB_1$ and 
	$(\tB_2\tB_1)(\tB_1\tB_2) = \tB_2\1\tB_2 = \1$, then we can conclude that $\tB_1\tB_2$ is unitary.  \carl{(It's a product
	of unitaries, so that step is immediate.)}
	Suppose the eigen-decomposition of $\tB_1\tB_2$ is
	\begin{align}
		\tB_1\tB_2 = \sum_{i=1}^m \lambda_i \ketbra{i}{i}
	\end{align}
	for some orthonormal set of eigenvectors $\{ \ket{i} \}_{i=1}^m$
	and $\norm{\lambda_i} =1$ for $1 \leq i \leq m$.
	Eq.~\ref{eq:eig_v} tells us that for each $1 \leq i \leq m$
	\begin{align*}
		\lambda_i + \lambda_i^{-1} = 2\Re(\lambda_i) = 2 \cos(2\mu),
	\end{align*}
	so we can conclude that $\lambda_i = e^{i 2\mu}$ or $e^{-i 2\mu}$.  \carl{Good proof (if you fill in the step at
	the beginning).}

%	\begin{align}
%		\ket{\tpsi} = \sum_{i=1}^m \frac{c_i}{\sqrt{2}} (\ket{u_{i,0}}\ket{u_{i,0}}+\ket{u_{i,1}}\ket{u_{i,1}}),
%	\end{align}
%	where $c_i$'s are coefficients such that $\sum_{i=1}^m \norm{c_i}^2 = 1$.
%	The special property of the subspace $V_i = \spn( \ket{u_{i,0}}, \ket{u_{i,1}})$ is that 
%	\begin{align*}
%	(\tilde{B}_0 + \tilde{B}_1) \ket{u_{i,0}} = 2\cos(-\pi/2d) \ket{u_{i,0}} 
%	&&(\tilde{B}_0 + \tilde{B}_1) \ket{u_{i,1}} = -2\cos(-\pi/2d) \ket{u_{i,1}}\\
%	(\tilde{B}_0 - \tilde{B}_1) \ket{u_{i,0}} = 2\sin(-\pi/2d) \ket{u_{i,1}} 
%	&&(\tilde{B}_0 - \tilde{B}_1) \ket{u_{i,1}} = 2\sin(-\pi/2d) \ket{u_{i,0}}.
%	\end{align*}
%	It is straightforward to calculate that 
%	\begin{align*}
%		\tilde{B}_0\tilde{B}_1 \ket{u_{i,0}} = \cos(\pi/d) \ket{u_{i,0}} -\sin(\pi/d) \ket{u_{i,1}},&&
%		\tilde{B}_0\tilde{B}_1\ket{u_{i,1}} = \sin(\pi/d)\ket{u_{i,0}} + \cos(\pi/d) \ket{u_{i,1}},
%	\end{align*}
%	so we can conclude that 
%	\begin{align*}
%		&\tilde{B}_0\tilde{B}_1(\ket{u_{i,0}} + i\ket{u_{i,1}}) = e^{i \frac{\pi}{d}} (\ket{u_{i,0}} + i\ket{u_{i,1}}), &&
%		&\tilde{B}_0\tilde{B}_1(\ket{u_{i,0}} - i\ket{u_{i,1}}) = e^{-i \frac{\pi}{d}} (\ket{u_{i,0}} - i\ket{u_{i,1}}).
%	\end{align*}
%	Hence each $V_i$ is spanned by $\omega_d$-eigenvector and $\omega_d^{-1}$-eigenvector of $\tB_0\tB_1$.
\end{proof}

@@

It can be checked that $X = \Psi_1(x_1x_2) = \sum_{i=1}^{d-1} \omega_d^i \ketbra{x_i}{x_i}$ 

@@

	U =\Psi_1(u) = \Psi_1(x_3x_4) =  \sum_{i=1}^{d-1} \ketbra{x_{i/r \pmod{d}}}{x_i}.

@@

@@

	UB_2U\ct = \sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct = \sum_{i=1}^{d-1} \ketbra{x_{i/r \pmod{d}}}{x_{(d-i)/r \pmod{d}}}.

@@

Let $i_1 = i/r \pmod{d}$ and $i_2  = (d-i)/r \pmod{d}$, then

@@

	i_1 + i_2 \equiv& \frac{i}{r} + \frac{d-i}{r} \pmod{d} \\
	\equiv& \frac{d}{r} \pmod{d}.

@@

Suppose $d/r \pmod{d} \equiv x$ for some integer $x$, then

@@

	rx \equiv d \pmod{d}.

@@

Since $d$ is a odd prime number and $r < d$, then $r$ cannot divide $d$, so $x = 0$ or $d$.
Considering the fact that $1 \leq i_1 \leq d-1$ and $1 \leq i_2 \leq d-1$, we know $x = i_1+i_2 = d$.

@@

Now suppose for $1 \leq i < i' \leq d-1$ and $U\ketbra{x_i}{x_{d-i}}U\ct = U\ketbra{x_i'}{x_{d-i'}}U\ct$,
it means that $i/r \equiv i'/r \pmod{d}$, which further implies that $i = i'$.
To conclude, conjugation by $U$ only permutes the terms of $B_2$, so

@@

Suppose the quantum strategy $(\ket{\psi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_{y \in [2]}\}$ achieves that 
$\bra{\psi} \bar{\I}_\alpha \ket{\psi} \leq \epsilon$.
The second step is to establish bounds of the following form
\begin{align}
	&\|(\tilde{Z}_A-\tilde{Z}_B)\ket{\psi}\| \leq c_1 \sqrt{\epsilon}\\
	&\|(\tilde{X}_A(\1+\tilde{Z}_B)-\tilde{X}_B(\1-\tilde{Z}_A))\ket{\psi}\| \leq c_2 \sqrt{\epsilon}\\
	&\|(\tilde{X}_A-\tilde{X}_B)\ket{\psi}\| \leq c_3 \sqrt{\epsilon}\\
	&\|(\tilde{Z}_A\tilde{X}_A+\tilde{X}_A\tilde{Z}_A)\ket{\psi}\| \leq c_4 \sqrt{\epsilon}.
\end{align}
Now we write $s = \sin(\mu)$, $c = \cos(\mu)$ and define
\begin{align*}
	S_1 &= \frac{\sqrt{s}}{2} \bar{\I}_\alpha, \quad
	S_2 = \sqrt{s}c(\tilde{Z}_A\tilde{X}_B+\tilde{X}_A\tilde{Z}_B),\\
	S_3 &= \frac{c}{\sqrt{s}}(\tilde{Z}_A-\tilde{Z}_B),\quad
	S_4 = \sqrt{s}(\tilde{X}_A-\tilde{X}_B)
\end{align*}
then $\bar{\I}_\alpha = S_1^2 + S_2^2 = S_3^2 + S_4^2$ and $\bra{\psi}\bar{\I}_\alpha \ket{\psi} \leq \epsilon$ implies that 
$\bra{\psi}S^2_i \ket{\psi} \leq \epsilon$ and $\|S_i \ket{\psi} \| \leq \sqrt{\epsilon}$ for $i = 1,2,3,4$.
We can easily check that 
\begin{align*}
	c_1 = \frac{\sqrt{s}}{c}, \quad
	c_2 = \frac{1}{\sqrt{s}} + \frac{1}{c\sqrt{s}}, \quad
	c_3 = \frac{1}{\sqrt{s}}.
\end{align*}
where we use the relation that $\tilde{X}_A(\1+\tilde{Z}_B)-\tilde{X}_B(\1-\tilde{Z}_A) = S_4/s^{1/2} + S_2/(cs^{1/2})$.
To calculate $c_4$, we use the relation
\begin{align}
	\tilde{Z}_A\tilde{X}_A + \tilde{X}_A\tilde{Z}_A = \frac{S_2}{c\sqrt{s}} + \frac{\sqrt{s}\tilde{X}_AS_3}{c} + \frac{\tilde{Z}_AS_4}{\sqrt{s}}
\end{align}
and reach the conclusion that  
\begin{align}
	c_4 = \frac{1+c+s}{c\sqrt{s}}
\end{align}
where we use that fact that $\tilde{Z}_A, \tilde{X}_A$ are unitaries.

>>>>

% Group
\newcommand{\Zd}{\Z_d^{\times}}

@@

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{EPR^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\G}{G}
\newcommand{\LS}{LS}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tZ}{\tilde{Z}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}
\newcommand{\dr}[1]{d^{(#1)}}

@@

We use some basic number theory in our work. A primitive root of a prime number
$d$ is an integer $r$ such that $r \pmod{d}$ has multiplicative order $d-1$. Equivalently,
$r$ is the generator of the multiplicative group of integers modulo $d$, $\Zd$ where
$\Zd = \{1,2\dots d-1\}$. \textcolor{red}{When the prime number $d$ has multiple primitive roots,
we always work with the smallest one.}
\carl{I'm not clear on what that last sentence means.  You just defined what a primitive root
is --- are you changing the definition now?}

@@

%======================================
\section{The extended weighted CHSH test}
\label{sec:chsh}
%======================================
Before introducing the extended weighted CHSH test, we fill in some background about the weighted CHSH inequality,
namely, that its maximal violation can self-test $2$-dimensional EPR pair and rotated Pauli operators.
The robust self-testing result is summarized in the following theorem.
\begin{theorem}
\label{thm:selftest}
	Suppose the quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]+1}, \{\tilde{B}_y\}_{y \in [2]+1})$ achieves the violation
	at least $2\sqrt{1+\alpha^2} - \epsilon$
	for some $\epsilon$, then
	there exists a local isometry $\Phi = \Phi_A \x \Phi_B$ and an auxiliary state $\ket{aux}$  such that
		\| \Phi( \tilde{A}_x \x \tilde{B}_y \ket{\psi}) -\ket{junk} \x (A_x \x B_y) \ket{\EPR{2}}  \| = O((\alpha+\frac{1}{\alpha}) \sqrt{\epsilon})
	for $x,y \in \{0, 1, 2\}$ where the subscript $0$ refers to the identity operator and $A_x, B_y$ are 
	defined in \cref{def:ideal}.  \carl{You're using both ``aux'' and ``junk'' for the auxilliary state.  Also you need
	to be clearer about what label you are using for Alice's and Bob's systems (see my previous comment on this).}
\end{theorem}
Our approach is very similar to the one used in Ref.~\cite{bamps2015} so we 
defer the proof of \cref{thm:selftest} till \cref{sec:selftest}.
After proving the robust self-testing result, we take one step further and observe an interesting property of the 
product of Bob's observables.
\begin{proposition}
\label{prop:2d-subspace}
	Let $\mu = \arctan(1/\alpha)$ for some $\alpha$.
	If a quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]+1}, \{\tilde{B}_y\}_{y \in [2]+1})$ achieves the maximal 
	violation of  $\I_{\alpha}$, then \hf{the only eigenvalues of $\tilde{B}_0\tilde{B}_1$ on the support of 
	$\tilde{\rho}_B = \Tr_A(\ketbra{\tpsi}{\tpsi})$
	are $e^{i2\mu}$ and $e^{-i2\mu}$.}  \carl{Make clear
	that we mean that these are the only eigenvalues.}
\end{proposition}
\begin{proof}[Proof of \cref{prop:2d-subspace}]
	Following the argument in the proof of \cref{thm:selftest} in \cref{sec:selftest}, we define
	\tilde{Z}_A = \tA_1, &&
	\tilde{Z}_B = (\tB_1+\tB_2)/2\cos(\mu).
	Substituting $\epsilon = 0$ into \cref{eq:zazb} we know that 
		\tZ_B \ket{\tpsi} = \tZ_A \ket{\psi}.
	Using this relation, we get
		\tZ_B^2\ket{\tpsi} = \tZ_B \tZ_A\ket{\tpsi} = \tZ_A \tZ_B \ket{\tpsi} = \tZ_A^2 \ket{\tpsi} = \ket{\tpsi},
	where we also use the facts that $\tZ_A$ and $\tZ_B$ commute and $\tZ_A^2 = A_1^2 = \1$.
	Hence we can conclude that $\tZ_B^2 =\1$ on $\supp(\tilde{\rho}_B)$.
	Expanding $\tilde{Z}_B^2$ we get
		\1 = \tilde{Z}_B^2 = \frac{\tB_1^2 + \tB_1\tB_2 + \tB_2\tB_1 + \tB_2^2}{4\cos(\mu)^2}
		=\frac{2\1 + \tB_1\tB_2 + \tB_2\tB_1}{4\cos^2(\mu)},
	so we can derive that 
	\label{eq:eig_v}
		\tB_1\tB_2 + \tB_2\tB_1 = 2(2\cos^2(\mu)-1)\1 = 2 \cos(2\mu) \1.
	\hf{Since $\tB_1\tB_2$ is the product of two unitaries,}
	we can assume the eigen-decomposition of $\tB_1\tB_2$ is
		\tB_1\tB_2 = \sum_{i=1}^m \lambda_i \ketbra{i}{i}
	for some orthonormal set of eigenvectors $\{ \ket{i} \}_{i=1}^m$
	and $\norm{\lambda_i} =1$ for $1 \leq i \leq m$.
	Eq.~\ref{eq:eig_v} tells us that for each $1 \leq i \leq m$
		\lambda_i + \lambda_i^{-1} = 2\Re(\lambda_i) = 2 \cos(2\mu),
	so we can conclude that $\lambda_i = e^{i 2\mu}$ or $e^{-i 2\mu}$.	
%	\begin{align}
%		\ket{\tpsi} = \sum_{i=1}^m \frac{c_i}{\sqrt{2}} (\ket{u_{i,0}}\ket{u_{i,0}}+\ket{u_{i,1}}\ket{u_{i,1}}),
%	\end{align}
%	where $c_i$'s are coefficients such that $\sum_{i=1}^m \norm{c_i}^2 = 1$.
%	The special property of the subspace $V_i = \spn( \ket{u_{i,0}}, \ket{u_{i,1}})$ is that 
%	\begin{align*}
%	(\tilde{B}_0 + \tilde{B}_1) \ket{u_{i,0}} = 2\cos(-\pi/2d) \ket{u_{i,0}} 
%	&&(\tilde{B}_0 + \tilde{B}_1) \ket{u_{i,1}} = -2\cos(-\pi/2d) \ket{u_{i,1}}\\
%	(\tilde{B}_0 - \tilde{B}_1) \ket{u_{i,0}} = 2\sin(-\pi/2d) \ket{u_{i,1}} 
%	&&(\tilde{B}_0 - \tilde{B}_1) \ket{u_{i,1}} = 2\sin(-\pi/2d) \ket{u_{i,0}}.
%	\end{align*}
%	It is straightforward to calculate that 
%	\begin{align*}
%		\tilde{B}_0\tilde{B}_1 \ket{u_{i,0}} = \cos(\pi/d) \ket{u_{i,0}} -\sin(\pi/d) \ket{u_{i,1}},&&
%		\tilde{B}_0\tilde{B}_1\ket{u_{i,1}} = \sin(\pi/d)\ket{u_{i,0}} + \cos(\pi/d) \ket{u_{i,1}},
%	\end{align*}
%	so we can conclude that 
%	\begin{align*}
%		&\tilde{B}_0\tilde{B}_1(\ket{u_{i,0}} + i\ket{u_{i,1}}) = e^{i \frac{\pi}{d}} (\ket{u_{i,0}} + i\ket{u_{i,1}}), &&
%		&\tilde{B}_0\tilde{B}_1(\ket{u_{i,0}} - i\ket{u_{i,1}}) = e^{-i \frac{\pi}{d}} (\ket{u_{i,0}} - i\ket{u_{i,1}}).
%	\end{align*}
%	Hence each $V_i$ is spanned by $\omega_d$-eigenvector and $\omega_d^{-1}$-eigenvector of $\tB_0\tB_1$.
\end{proof}

@@

It can be checked that $X = \Psi_1(x_1x_2) = \sum_{i \in \Zd} \omega_d^i \ketbra{x_i}{x_i}$ 

@@

	U =\Psi_1(u) = \Psi_1(x_3x_4) =  \sum_{i \in \Zd} \ketbra{x_{r^{-1}i}}{x_i},

@@

\hf{where $r^{-1}$ is the multiplicative inverse of $r$ in $\Zd$.
All the multiplications done on the label $i$ of the state $\ket{x_i}$ are within the group $\Zd$.}

@@

	UB_2U\ct = \sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct = \sum_{i=1}^{d-1} \ketbra{x_{r^{-1} i}}{x_{r^{-1}(d-i)}}.

@@

Let $i_1 = i r^{-1} \in \Zd$ and $i_2  = r^{-1} (d-i) \in \Zd$, then

@@

	r(i_1 + i_2) \equiv  i + (d-i) \equiv d \pmod{d} .

@@

Let $i_1 + i_2= x \in \{2, 3 \dots 2d-2\}$, then

@@

	rx \equiv d \pmod{d}

@@

Since $d$ is an odd prime number and $r < d$, then $r$ cannot divide $d$ and the only valid value of $x$ is $d$.

@@

Now suppose for some $1 \leq i < i' \leq d-1$ and $U\ketbra{x_i}{x_{d-i}}U\ct = U\ketbra{x_{i'}}{x_{d-i'}}U\ct$,
it means that in $\Zd$, $i r^{-1} = i' r^{-1}$ and $i = i'$, which contradicts the fact that $i \neq i'$.
What we have shown so far is that conjugation by $U$ only permutes the terms of $B_2$, so

@@

Suppose the quantum strategy $(\ket{\psi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_{y \in [2]}\}$ achieves that 
$\bra{\psi} \bar{\I}_\alpha \ket{\psi} \leq \epsilon$.
The second step is to establish bounds of the following form
\begin{align}
	\label{eq:zazb} &\|(\tilde{Z}_A-\tilde{Z}_B)\ket{\psi}\| \leq c_1 \sqrt{\epsilon}\\
	&\|(\tilde{X}_A(\1+\tilde{Z}_B)-\tilde{X}_B(\1-\tilde{Z}_A))\ket{\psi}\| \leq c_2 \sqrt{\epsilon}\\
	&\|(\tilde{X}_A-\tilde{X}_B)\ket{\psi}\| \leq c_3 \sqrt{\epsilon}\\
	&\|(\tilde{Z}_A\tilde{X}_A+\tilde{X}_A\tilde{Z}_A)\ket{\psi}\| \leq c_4 \sqrt{\epsilon}.
\end{align}
Now we write $s = \sin(\mu)$, $c = \cos(\mu)$ and define
\begin{align*}
	S_1 &= \frac{\sqrt{s}}{2} \bar{\I}_\alpha, \quad
	S_2 = \sqrt{s}c(\tilde{Z}_A\tilde{X}_B+\tilde{X}_A\tilde{Z}_B),\\
	S_3 &= \frac{c}{\sqrt{s}}(\tilde{Z}_A-\tilde{Z}_B),\quad
	S_4 = \sqrt{s}(\tilde{X}_A-\tilde{X}_B)
\end{align*}
then $\bar{\I}_\alpha = S_1^2 + S_2^2 = S_3^2 + S_4^2$ and $\bra{\psi}\bar{\I}_\alpha \ket{\psi} \leq \epsilon$ implies that 
$\bra{\psi}S^2_i \ket{\psi} \leq \epsilon$ and $\|S_i \ket{\psi} \| \leq \sqrt{\epsilon}$ for $i = 1,2,3,4$.
We can easily check that 
\begin{align*}
	c_1 = \frac{\sqrt{s}}{c}, \quad
	c_2 = \frac{1}{\sqrt{s}} + \frac{1}{c\sqrt{s}}, \quad
	c_3 = \frac{1}{\sqrt{s}}.
\end{align*}
where we use the relation that $\tilde{X}_A(\1+\tilde{Z}_B)-\tilde{X}_B(\1-\tilde{Z}_A) = S_4/s^{1/2} + S_2/(cs^{1/2})$.
To calculate $c_4$, we use the relation
\begin{align}
	\tilde{Z}_A\tilde{X}_A + \tilde{X}_A\tilde{Z}_A = \frac{S_2}{c\sqrt{s}} + \frac{\sqrt{s}\tilde{X}_AS_3}{c} + \frac{\tilde{Z}_AS_4}{\sqrt{s}}
\end{align}
and reach the conclusion that  
\begin{align}
	c_4 = \frac{1+c+s}{c\sqrt{s}}
\end{align}
where we use that fact that $\tilde{Z}_A, \tilde{X}_A$ are unitaries.
